Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added more calculations to sha256d estimate

\subsection{Estimates}

We see in Tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-\ac{LAFS} uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have a benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume a worst case scenario of hashing 32 bytes, where the cycles per
byte count is exactly the same as for 8 bit median, we get:

$$\frac{median * size + 179.62*32}{size} = SHA256d\ estimate$$

@@

Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. For shorter lengths of data,
more of the candidates are faster than double \ac{SHA}-256. Nevertheless, given
the practical situation that Tahoe-\ac{LAFS} is a file system, most files
processed will be larger than the file sizes estimated here. Not all hashing
operations in Tahoe-\ac{LAFS} are strictly dependant on the original file size,
which would mean that all candidates would have a chance of outperforming double
\ac{SHA}-256. This estimate is however worst case, which leads us to believe
that at least for larger input sizes (i.e. over 1536 bytes) only the five
fastest candidates will have a chance of outperforming double \ac{SHA}-256.

>>>>

\subsection{Double SHA-256 Estimates}
\ac{SUPERCOP} does not measure the speed of double \ac{SHA}-256, so we have no exact
value of how many cycles this should take, we can however estimate it. For every hash
calculation double \ac{SHA}-256 will have to hash an extra 32-byte.
\ac{SUPERCOP} does not give results for hashing 32-byte, so this will also have
to be estimated. The calculations of worst-case scenario (cycles/byte for 32
byte is the same as 8 byte), best-case (cycles/byte for 32 byte is the same as
for 64 byte) and interpolation (assuming linear decrease) are shown in Table
\ref{tbl:supercop:sha256d}. The calculation for this table are as follows:

$$\frac{median * size + 179.62*32}{size} = SHA256d\ estimate (worst-case)$$

$$\frac{median * size + 38.12*32}{size} = SHA256d\ estimate (best-case)$$

$$179.62 + \frac{38.12-179.62}{64-8}*(32-8) = 118.97 (cycles/byte for 32 byte)$$

$$\frac{median * size + 118.97*32}{size} = SHA256d\ estimate (interpolation)$$

@@

Interpolation gives a somewhat pessimistic result of the cycles/byte needed for
hashing 32 byte, so the probable speed is somewhere in between the
interpolation point and the best case time.

### 2010-12-14 paper/tables/supercop_sha256d.tex
Changed supercop double sha256 to worst-case scenario
Added more calculations to sha256d estimate

\begin{table}
  \centering
  \begin{tabular}{ | c | c | }
    \hline
    \textbf{Size} & \textbf{Median} \\ \hline
    8    & 655.54 \\ \hline
    64   & 97.61 \\ \hline
    576  & 24.66 \\ \hline
    1536 & 18.93 \\ \hline
    4096 & 16.76 \\ \hline
  \end{tabular}
  \caption{Estimates for double SHA-256}
  \label{tbl:supercop:sha256d}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{ | c | c | c | c |}
    \hline
    \textbf{Size} & \textbf{Worst case} & \textbf{Interpolation} & \textbf{Best case} \\ \hline
    8    & 898.1  & 655.53  & 332.10 \\ \hline
    64   & 127.93 & 97.61  & 57.18 \\ \hline
    576  & 53.85  & 24.66  & 20.17 \\ \hline
    1536 & 20.19  & 18.89  & 17.23 \\ \hline
    4096 & 17.23  & 16.76  & 16.13 \\ \hline
  \end{tabular}
  \caption{Estimates for medians using double \ac{SHA}-256}
  \label{tbl:supercop:sha256d}
\end{table}
